### 2018-07-08 article.tex
Analiza.

@@

\begin{itemize}
	\item - akumulacja wsparć,
	\item - akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
	\item - akumulacja ważona po wzorcach, przez kontrast,
	\item - akumulacja znormalizowanych wag członków,
	\item - iloczyn znormalizowanych wag i kontrastu
\end{itemize}

@@

Wybrane zbiory danych.

@@

>>>>

\begin{algorithm}
\caption{Training classifier ensemble from multiple balanced training datasets separated from one imbalanced dataset of binary problem}\label{alg:moore}
Given a dataset $DS$:
\begin{enumerate*}
	\item Divide $DS$ into subsets of minority- $MinC$ and majority-class $MajC$
	\item Calculate imbalanced ratio $IR$ as the proportion of the number of patterns in $MinC$ and $MajC$ 
	\item Establish $k$ by rounding $IR$ to nearest integer
	\item Perform a \emph{shuffled k-fold division} of $MajC$ to produce a set of subsets $MajC_1, MajC_2, \ldots, MajC_k$ 
	\item For every $i$ in range to $k$
	\begin{enumerate*}
		\item Join $MajC_i$ with $MinC$ to prepare a training set $TS_i$,
		\item Train classifier $\Psi_i$ on $TS_i$ and add it into ensemble
	\end{enumerate*}
\end{enumerate*}
\end{algorithm}

@@

\begin{itemize}
	\item - reg akumulacja wsparć,
	\item - wei akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
	\item - con akumulacja ważona po wzorcach, przez kontrast,
	\item - nor akumulacja znormalizowanych wag członków,
	\item - nci iloczyn znormalizowanych wag i kontrastu
\end{itemize}

@@

For the experimental evaluation of the proposed method, a collection of data sets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}. From among the available datasets, 40 were selected presenting only binary problems with quantitative attributes. A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table 1.

\begin{table}[!h]
\footnotesize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1}
\begin{tabular}{@{}|rl|c|ccc|c|}\hline%

\multirow{2}{*}{\bfseries \#} &
\multirow{2}{*}{\bfseries Dataset} &
\multirow{2}{*}{\bfseries Features} &
\multicolumn{3}{c|}{\bfseries Samples} &
\multirow{2}{*}{\bfseries \textsc{ir}} 	
\\

& & & 
\multicolumn{1}{c}{\textsc{all}} & 
\multicolumn{1}{c}{\textsc{maj}} & 
\multicolumn{1}{c|}{\textsc{min}} &

	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/datasets.csv}{}%
	{

	\idx & \multicolumn{1}{l|}{\emph{\dbname}} & \features & 
	\multicolumn{1}{c}{\samples} & 
	\multicolumn{1}{c}{\majority} & 
	\multicolumn{1}{c|}{\minority} & \ir

	}%
\end{tabular}
\caption{Summary of imbalanced datasets chosen for evaluation}
\end{table}

As may be observed after the Table analysis, the experiments will be based on data sets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}.

@@

\begin{itemize}
	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) ---
	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) ---
	\item \emph{Decision Tree Classifier} (\textsc{dtc}) ---
\end{itemize}

### 2018-07-08 figures/ensemble_scheme.tex
Analiza.

% Original training set with division
\node[el, minimum width=6cm](its) at (0,0) {Imbalanced training set};
\node[el, text width=.5cm] (minc) at (-2.5, -1.5) {\tiny Min. class};
\node[el, minimum width = 4.5cm] (majc) at (.75, -1.5) {\tiny Majority class};

% Pre-methods
\node[el, thick, minimum width = 4.5cm, minimum height = .5cm] (kfold) at (.75, -2.5)
{\scriptsize \textsc{shuffled k-fold division}};
\node[el, thick, minimum width = 2cm, minimum height = .5cm] (oversampling) at (5, -2.5)
{\tiny \textsc{oversampling}};

% Processed training sets
\node[el, text width=.5cm] (majc0) at (-1, -3.5) {\tiny Maj. \#0};
\node[el, text width=.5cm] (majc1) at (.5, -3.5) {\tiny Maj. \#1};
\node[el, text width=.5cm] (majck) at (2.5, -3.5) {\tiny Maj. \#k};
\node[el, text width=.5cm] (minc0) at (-1, -4.5) {\tiny Min. class};
\node[el, text width=.5cm] (minc1) at (.5, -4.5) {\tiny Min. class};
\node[el, text width=.5cm] (minck) at (2.5, -4.5) {\tiny Min. class};

@@

% Member classifiers
\node[el] (c0) at (-1, -6) {$\Psi_1$};
\node[el] (c1) at (.5, -6) {$\Psi_2$};
\node[el] (ck) at (2.5, -6) {$\Psi_k$};
\node[el, minimum width=2cm] (co) at (5, -6) {$\Psi_{os}$};

@@

\node[el] (s0) at (-1, -9.5) {$s_1$};
\node[el] (s1) at (.5, -9.5) {$s_2$};
\node[el] (sk) at (2.5, -9.5) {$s_k$};
\node[el, minimum width=2cm] (so) at (5, -9.5) {$s_{os}$};

\node[el, minimum width=7.5cm, minimum height = .5, thick](fuser) at (2.25,-10.75)
{\textsc{fuser}};

@@

\draw[->] (minc.south) |- (minc0.west);
\draw[<->] (minc0) -- (minc1);
\draw[<->] (minc1) -- (minck);
\node[text width = 1cm] at (1.7,-4)
{\bfseries . . .};

>>>>

% Original training set with division
\node[el, minimum width=6cm](its) at (0,0) {Imbalanced training set};
\node[el, text width=.75cm] (minc) at (-2.5, -1.5) {\tiny $MinC$};
\node[el, minimum width = 4.5cm] (majc) at (.75, -1.5) {\tiny $MajC$};

% Pre-methods
\node[el, thick, minimum width = 4.5cm, minimum height = .5cm, rounded corners=2mm] (kfold) at (.75, -2.5)
{\scriptsize \textsc{shuffled k-fold division}};
\node[el, thick, minimum width = 2cm, minimum height = .5cm, rounded corners=2mm] (oversampling) at (5, -2.5)
{\tiny \textsc{oversampling}};

% Processed training sets
\node[el, text width=.75cm] (majc0) at (-1, -3.5) {\tiny$MajC_0$};
\node[el, text width=.75cm] (majc1) at (.5, -3.5) {\tiny$MajC_1$};
\node[el, text width=.75cm] (majck) at (2.5, -3.5) {\tiny$MajC_k$};
\node[el, text width=.75cm] (minc0) at (-1, -4.5) {\tiny$MinC$};
\node[el, text width=.75cm] (minc1) at (.5, -4.5) {\tiny$MinC$};
\node[el, text width=.75cm] (minck) at (2.5, -4.5) {\tiny$MinC$};
\node[text width = 1cm] at (1.65,-4)
{\bfseries . . .};

@@

% Member classifiers
\node[el, rounded corners=5mm] (c0) at (-1, -6) {$\Psi_1$};
\node[el, rounded corners=5mm] (c1) at (.5, -6) {$\Psi_2$};
\node[el, rounded corners=5mm] (ck) at (2.5, -6) {$\Psi_k$};
\node[el, minimum width=2cm, rounded corners=5mm] (co) at (5, -6) {$\Psi_{os}$};

\node[text width = 1cm] at (1.65,-6)
{\bfseries . . .};

@@

\node[el] (s0) at (-1, -9.5) {$s_1$};
\node[el] (s1) at (.5, -9.5) {$s_2$};
\node[el] (sk) at (2.5, -9.5) {$s_k$};
\node[el, minimum width=2cm] (so) at (5, -9.5) {$s_{os}$};
\node[text width = 1cm] at (1.65,-9.5)
{\bfseries . . .};

\node[el, minimum width=7.5cm, minimum height = .5, thick, rounded corners=2mm](fuser) at (2.25,-10.75)
{\textsc{fuser}};

@@

\draw[->] (minc.south) |- (minc0.west);
\draw[<->] (minc0) -- (minc1);
\draw[<->] (minc1) -- (minck);
